---
title: "Exercise1:Sex-dimorphic Gene Expression of a Specific Gene Across Species"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### **Sex dimorphic constitutive gene expression in eight Drosophila species.**

#### Step1: Load Library

```{r cars}
#load necessary library
library(dplyr)
library(ggplot2)
```

#### Step2: Choose Data for model organism *D. melanogater*

```{r cars2}
#Prepare Input data
df_model <- read.csv(file.choose()) # choose the data for model organism
head(df_model) #check
nrow(df_model) #check
```

#### Step3: Choose Data for non-model organism


```{r cars3}
df_non_model <- read.csv(file.choose()) # choose the data for non-model organism
head(df_non_model) #check
nrow(df_non_model) #check
```

#### Step4: Choose Your Gene and Replace in the SYMBOL == "Gs1"

```{r cars4}
#Selecting the rows for the specific gene 

df_model_Gene <- subset(df_model, SYMBOL == "Gs1",
                  select=c(mean.nrc.f,mean.nrc.m))

head(df_model_Gene) #check

df_non_model_Gene <- subset(df_non_model, SYMBOL_DMel == "Gs1",
                   select=c(mean.nrc.f,mean.nrc.m))

head(df_non_model_Gene) #check
```

#### Step5: Create data frames for model organsim

```{r cars5}
#Create data frames

#model organisms 
df3_model_Gene <- data.frame(
  NRC = c(df_model_Gene$mean.nrc.m),
  Species = c("D. melanogater"),
  Sex = c("M")
)

df4_model_Gene <- data.frame(
  NRC = c(df_model_Gene$mean.nrc.f),
  Species = c("D. melanogater"),
  Sex = c("F")
)

```

#### Step6: Create data frames for non-model organsim

```{r cars6}
#non-model organism 
df3_non_model_Gene <- data.frame(
  NRC = c(df_non_model_Gene$mean.nrc.m),
  Species = c("D. ananassae"),
  Sex = c("M")
)

df4_non_model_Gene <- data.frame(
  NRC = c(df_non_model_Gene$mean.nrc.f),
  Species = c("D. ananassae"),
  Sex = c("F")
)
```

#### Step7: Merge the model and non-model organsim data frames

```{r cars7}
#merge the data frame 

df_mel <- bind_rows(df3_model_Gene,df4_model_Gene)
df_ana <- bind_rows(df3_non_model_Gene,df4_non_model_Gene)
df_for_plot <- bind_rows(df_mel,df_ana)

```

#### Step8: Choose Your Headers


```{r cars8}
#Change the header 

names(df_for_plot)[1] <- "Read_Counts"
names(df_for_plot)[2] <- "Species"
names(df_for_plot)[3] <- "Sex"
head(df_for_plot)
```

## Make Your Plots to see the Sex Biased Gene Expression

```{r pressure, echo=FALSE}

p <- ggplot(data=df_for_plot, aes(x=Species, y=Read_Counts, fill=Sex, label=Read_Counts)) +
  geom_bar(stat="identity") +
  geom_text(size = 3.0, position = position_stack(vjust = 0.5))+
  scale_fill_manual(values = c("firebrick","dodgerblue4"))
p1 <- p + theme(axis.text.x = element_text(angle = 0))

p1
```
